Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-05-20 papers/paper-eccentricity/sections/numerical.tex
Small edits to discussion

\subsection{Assessing Eccentricity Uncertainty}
In our analysis, we wish to determine the population spread in eccentricity from a finite set of observations.
We assess the uncertainty in eccentricity using two methods: an inverse modelling approach and a forward modelling approach.

The first method follows \citet{nasim2020}, and is an inverse problem. 
For each simulation in a given set, we determine the mean eccentricity $e_\mathrm{h}$ over five orbital periods centred on the orbit within which the SMBH binary has become hard.
The binary hardening radius $a_\mathrm{h}$ is defined as \citep[e.g.][]{merritt2013}
\begin{equation}\label{eq:ahard}
    a_\mathrm{h} = \frac{q}{1+q} \frac{r_\mathrm{h}}{4},
\end{equation}
where $r_\mathrm{h}=r(m<2M_{\bullet,1})$ is the influence radius and $q = \{q \in \mathbb{R} | 0<q \leq 1\}$ is the mass ratio between the SMBHs.
Under the assumption that each calculated mean eccentricity is a sample of some common distribution, we may (assuming that the distribution is Gaussian) obtain an estimate of the standard deviation of this distribution by taking the standard deviation of the collection of sample eccentricity means.

>>>>

\subsection{Assessing Eccentricity Uncertainty}
In our analysis, we wish to determine the population spread in eccentricity from a finite set of observations.
We assess the uncertainty in eccentricity using an inverse modelling approach following \citet{nasim2020}. 
For each simulation in a given set, we determine the mean eccentricity $e_\mathrm{h}$ over five orbital periods centred on the orbit within which the SMBH binary has become hard.
The binary hardening radius $a_\mathrm{h}$ is defined as \citep[e.g.][]{merritt2013}
\begin{equation}\label{eq:ahard}
    a_\mathrm{h} = \frac{q}{1+q} \frac{r_\mathrm{h}}{4},
\end{equation}
where $r_\mathrm{h}=r(m<2M_{\bullet,1})$ is the influence radius and $q = \{q \in \mathbb{R} | 0<q \leq 1\}$ is the mass ratio between the SMBHs.
Under the assumption that each calculated mean eccentricity is a sample of some common distribution, we may (assuming that the distribution is Gaussian) obtain an estimate of the standard deviation of this distribution by taking the standard deviation of the collection of sample eccentricity means.
